---
title: "Job scripts for a simulation study"
subtitle: "USERCHOICE - replace with your project name"
author: "USERCHOICE - replace with your name"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

These scripts are intended to be run in the following order:

1. CreateDatasets.R
2. FitModel.R
3. LoadStackAndSave.R
4. ZipAndDelete
5. (if necessary) UnzipAndRestore.R

Each can be run in RStudio's Jobs pane using commands like this from the `rstudioapi` package:

```{r, eval=FALSE}
rstudioapi::jobRunScript(
  path = paste0(job_script_dir, "CreateDatasets.R"),
  name = "CreateDatasets - Scenario 1a",
  workingDir = paste0(simulation_root, "Scenario1a/")
)
```

or on a PBS cluster using a job file like 

```
#PBS -l walltime=01:00:00
#PBS -m aeb
#PBS -M joe.bloggs@ucb.com
cd Scenario1a/
/opt/R/4.0.1/bin/Rscript ../JobScripts/CreateDatasets.R
```

or in batch mode on a Windows machine using commands like:

```
cd Scenario1a/
"C:\Program Files\R\R-3.6.1\bin\Rscript" ..\JobScripts\CreateDatasets.R
```

Obviously, in each of the examples above, you should:

* change the R version to match that of your target system;
* change the scenario path as appropriate for your project. 
